Tagging variables with keywords

### 2020-07-17 data-raw/variable-keywords.Rmd
var_label_normalize

```{r}
metadata_database <- readRDS( file.path('../data-raw', 'eb_metadata_database_20200628.rds'))
```

@@

  # clean up variable labels to unify the spelling of certain common words and abbreviation
  mutate(
    var_id = paste0(filename, " ", var_name_orig),
    var_label_norm1 = gsub(
      "^cap_", "common-agricultural-policy_", var_label_norm),
    var_label_norm1 = gsub(
      "_cap_", "_common-agricultural-policy_", var_label_norm),

@@

    # replace underscore with space
    text = gsub("_", " ", var_label_norm1)) %>%
  ungroup() %>%
  # select the needed variables
  select(filename, qb, var_label_norm1, var_label_orig, var_id, text)
```

>>>>

```{r}
metadata_database <- readRDS( file.path('..', 'data-raw', 'eb_metadata_database_20200628.rds'))
```

@@

  # clean up variable labels to unify the spelling of certain common words and abbreviation
  #
  #  FROM HERE on this is var_label_normalize()
  mutate(
    var_id = paste0(filename, " ", var_name_orig),
    var_label_norm1 = var_label_normalize(var_label_norm)
    ) %>%
  ungroup() %>%
  # select the needed variables
  select(filename, qb, var_label_norm1, var_label_orig, var_id, text)
```

```{r, eval = FALSE}
## went to var_label_normalize()
  mutate(
    var_id = paste0(filename, " ", var_name_orig),
    var_label_norm1 = gsub(
      "^cap_", "common-agricultural-policy_", var_label_norm),
    var_label_norm1 = gsub(
      "_cap_", "_common-agricultural-policy_", var_label_norm),

@@

    # replace underscore with space
    text = gsub("_", " ", var_label_norm1)) 
```
